A comprehensive study of the early phylodynamics of SARS-CoV-2 in Europe

### 2020-11-25 reports/paper/main.tex
new insights table

Comparison with ECDC case counts: delay in notifications and underreporting, for some of the  countries at the end of the peioord the reported cases are very closed to the trajectories, e.g. Italy, Germany. Hubei-China huge difference in tendency and absolute numbers.\\ \todo{Working on these with new analyses}

@@

>>>>

Comparison with ECDC case counts: delay in notifications and underreporting, for some of the  countries at the end of the periord the reported cases are very closed to the trajectories, e.g. Italy, Germany. Hubei-China huge difference in tendency and absolute numbers.\\ \todo{Working on these with new analyses}

@@

Measure expected day of introduction.
